The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-01-31 Text/paper.tex
added combined bot

\section{Experimental setup}
For the testing of the bots, multiple Schnapsen tournaments were held. Each bot played a 100 games against every other bot. The competing bots were:
\begin{itemize}
\item Minimax
\item Bully
\item Rand
\item Rdeep
\item KBBot
\item ML
\item MLAdvanced
\end{itemize}

Both ML, and MLAdvanced were trained on the same bot. First, bully, then rand, then rdeep, then kbbot, etc.

>>>>

\section{Experimental setup}
To answer our research question, multiple Schnapsen tournaments were held. Each machine-learning bot played multiple 120 game tournaments against each individual non-learning bot. Each learning bot played 9 tournaments with 3 different models against each static bot.
The non-machine learning opponents were:
 \begin{itemize}
\item Bully
\item Rand
\item Rdeep
\end{itemize}
The research procedure was as follows:
\begin{itemize}
\item Training
\item 120 game tournament
\item 120 game tournament
\item 120 game tournament
\end{itemize}

This procedure was repeated twice to reach the total of 9 tournaments respectively. The machine-learning bots did not compete against eachother.
Both ML, and MLAdvanced were trained on the same bot. First, bully, then rand, then rdeep, then kbbot, etc.
